\Ace: Growing A Statically-Typed Language Inside a Python

### 2014-03-24 ace-oopsla14/ace-oopsla14.tex
OOPSLA14 progress

\subsubsection{Dispatch Protocol}
\begin{codelisting}
\lstinputlisting{listing9.py}
\caption{\texttt{[}in \texttt{examples/clx.py]} The active type family \texttt{Ptr} implements the semantics of OpenCL pointer types.}
\label{cplx}
\end{codelisting}

\subsubsection{Typechecking}
When typechecking a compound expression or statement, the Ace compiler temporarily hands control to the object selected by the dispatch protocol by calling the method \verb|type_|$X$, where $X$ is  the name of the syntactic form, taken from the Python grammar \cite{python} (appended with a suffix in some cases).

@@

>>>>

\subsubsection{Dispatch Protocol}
\begin{codelisting}
\begin{lstlisting}
class RecordType(ace.Type):
  def __init__(self, sig):
    self.sig = sig

  def analyze_Dict(self, ctx, e, ty):
    ...

  def translate_Dict(self, ctx, e):
    ...

  def synthesize_Attribute(self, ctx, e): 
    ...

  def translate_Attribute(self, ctx, e):
    ...

  def trans_type(self, target):
    if target.supports(examples.fp.EagerTuple):
      return target.EagerTuple()
    else if isinstance(target, examples.py.Dyn):
      return target.Dyn()

record = ace.util.SlicesToOrderedDict(RecordType, 
  TypeFormationError("..."))
\end{lstlisting}
\caption{Records...}
\label{record}
\end{codelisting}
\subsubsection{Typechecking}
When typechecking a compound expression or statement, the Ace compiler temporarily hands control to the object selected by the dispatch protocol by calling the method \verb|type_|$X$, where $X$ is  the name of the syntactic form, taken from the Python grammar \cite{python} (appended with a suffix in some cases).

@@

\appendix
\section{Complex Numbers}
\begin{codelisting}
\lstinputlisting{listing9.py}
\caption{\texttt{[}in \texttt{examples/clx.py]} The active type family \texttt{Ptr} implements the semantics of OpenCL pointer types.}
\label{cplx}
\end{codelisting}
